A partisan affair: Mapping patronage in municipal bureaucracies of Brazil

### 2021-03-09 paper/draft.tex
fix party membership data
generate new visualizations of dollar amounts
incorporate info on party affiliation

@@

>>>>

Additionally, it is worthwhile noting that the affiliation of party members has been increasing over time. Importantly, this evolution has been rather rapid over time. While in the year 1997 there were around 200 thousand active party members, by the year 2018 this has increased to 10 million.

\begin{figure}[H]
    \centering
    \includegraphics[width = 10cm, height = 10cm]{figures/partisanship/plot_partisan_by_year.pdf}
    \caption{\textbf{Number of active party members by year}. There has been a rapid growth in the number of party members in the period between 1997 and 2020.}
    \label{fig:map_pooled}
\end{figure}

Another interesting feature to note in the data is that there are discontinuities in the number of party members. The dashed lines indicate the year of a local election in Brazil, such as 2002 or 2018. The jumps in party affiliation are expressive, in particular for earlier electoral cycles. In particular, for the electoral year of 2002, there were around 2 million new party members registered as a result of that particular local election. While these jumps have decreased in more recent elections, it is an empirical regularity that highlights the electoral motivation driving party affiliation in Brazil.

@@

\emph{perform an Oaxaca decomposition to understand the variant compensations}
